---
title: "Tutorial for lm_s"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The myRfunclm package only contains the lm_s function. It will fit a linear model using given data set and will automatically print summary of coefficients and anova table of the model. This is a mimic of the lm function in the basic R language.
This vignette shows how to use this function and compare it with the original R function.

To begin, we'll load package and build sample data set.

```{r setup}
library(myRfunclm)
set.seed(1010)
y = rnorm(1000)
x = matrix(rnorm(3000),1000,3)
data(mtcars)
d = mtcars
```

## `lm_s(formula, data)` : Fit linear model and print the summary of coefficients and anova table.

### Fit simple regression model:
```{r}
m = lm_s(y~x[,1])
```
Compared with the R lm function:
```{r}
m = lm(y~x[,1])
summary(m)
anova(m)
```

### Fit mutiple regression model:

```{r}
m = lm_s(y~x[,1]+x[,2]+x[,3])
```
Compared with the R lm function:
```{r}
m = lm(y~x[,1]+x[,2]+x[,3])
summary(m)
anova(m)
```

### Fit model form data set:
```{r}
m = lm_s(mpg~hp+wt,data = d)
```

